\sc Estimating Evolutionary Parameters for Low Complexity Regions using an Approximate Bayesian Computation

### 2023-01-17 thesis_template/paper0904.tex
Jan 13 updates - working on materials and methods
materials and methods update Jan 17

\lstset{style=mystyle}
% \usetikzlibrary{pgfplots.clickable}
% \usepgfplotslibrary{clickable}
% tables
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{multicol}
\usepackage{multirow}
% figs
%\usepackage{subfig}% http://ctan.org/pkg/subfig
\usepackage{subcaption}
%\newsubfloat{figure}% Allow sub-figures
\usepackage{caption}%lable fig caption as fig
%\captionsetup[subfigure]{labelfont=bf, justification=raggedright, labelformat=empty} %no caption label
\usepackage{stackengine} %places caption inside figure?
\captionsetup{subrefformat=parens} %when you reference the subcaption it will be (a) for example %{labelfont={color=blue}}
%\captionsetup[subfigure]{labelsep=colon}

@@

\section{Materials and Methods} 
\label{methods}
Custom scripts and commands utilized in this analysis can be found on \texttt{GitHub} at
\url{https://github.com/opticrom/abcmcmc-thesis4c12}.

@@

>>>>

\lstset{style=mystyle}
% \usetikzlibrary{pgfplots.clickable}
% \usepgfplotslibrary{clickable}
% tables
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{multicol}
\usepackage{multirow}
% figs
\captionsetup[figure]{labelfont={color=blue}, font={color=black}}
%\usepackage{subfig}% http://ctan.org/pkg/subfig
\usepackage{subcaption}
%\newsubfloat{figure}% Allow sub-figures
\usepackage{caption}%lable fig caption as fig
%\captionsetup[subfigure]{labelfont=bf, justification=raggedright, labelformat=empty} %no caption label
\usepackage{stackengine} %places caption inside figure?
\captionsetup{subrefformat=parens} %when you reference the subcaption it will be (a) for example %{labelfont={color=blue}}
%\captionsetup[subfigure]{labelsep=colon}

@@

\section{Materials and Methods (mid-year stuff)} 
\label{methods}
Custom scripts and commands utilized in this analysis can be found on \texttt{GitHub} at
\url{https://github.com/opticrom/abcmcmc-thesis4c12}.

@@

This study utilized the ABC Markov chain Monte Carlo algorithm which was originally proposed by \citet{marjoram2003markov} and later built upon in a subsequent paper \citep{marjoram2013approximation}. The algorithm begins from a randomly selected parameter value and follows the steps below.

\begin{figure}[h]
	\begin{enumerate}
		\item If now at $\theta$, propose a move to $\theta'$ according to a proposal distribution $q(\theta, \theta')$.
		\item Simulate a dataset, $D'$ using $\theta'$.
		\item If $D' ~ D$ proceed to step 4; else, output $\theta$ and return to 1.
		\item Calculate the Hastings Ratio.
		\item Accept, and output, the new $\theta'$ with probability h. Else return to, and output, $\theta$, Go back to 1.
	\end{enumerate}
	\label{fig:algorithm1}
	\caption{Hello}
\end{figure}
